---
title: "eds212-day5-Practice"
author: "Karol Paya"
execute: 
  warning: false
format: html
---

Hey this is Takeen
```{r}
#| message: false
#Load Libraries
library(tidyverse)
```


```{r}
#| include: false
# Reviewing the dataset
head(starwars)
head(starwars)
dim(starwars)
```

```{r}
#| echo: false
ggplot(data=starwars, aes(x=height, y=mass,color=mass)) + 
  geom_point() +
  labs(x="Height (cm)",
       y="Mass (Kg)", title=("Height Vs. Mass"))
```
-Create a histogram of character heights
-Update the fill color to purple and the outside border line of each histogram bin to orange
-update the axis labels
-update your code chunck options so that only your code and output graph appear in the rendered doc (no warnings or messages)
```{r}
#| fig-cap: "this is my figure caption"
#| fig-alt: "this is some alt text"
ggplot(data = starwars, aes(x = height)) + geom_histogram(fill ="purple", color="orange") + labs (x= "Height (cm)")
```

'df$col_name`

```{r}

sw_height_mean<-round(mean(starwars$height, na.rm=TRUE), 
                      digits=3)
```

The mean height of all starwars characters is `r sw_height_mean`

